Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2020-07-24 summary.Rmd
minor changes

---
title: "Clustering and Parameter Estimation for the Popularity Adjusted Block Model"
output:
  pdf_document:
    citation_package: natbib
    number_sections: yes
# output: html_document
# geometry: "left=1cm,right=1cm,top=1cm,bottom=1.5cm"
urlcolor: blue
header-includes:
- \usepackage{float}
- \usepackage{mathtools}
- \usepackage{natbib}
- \usepackage[linesnumbered,vlined,ruled]{algorithm2e} 
- \setcitestyle{numbers,square}
- \usepackage{verbatim}
bibliography: misc.bib
abstract: |
  In this paper, we connect two probabilistic models for graphs, the Popularity 
  Adjusted Block Model (PABM) and the Generalized Random Dot Product Graph 
  (GRDPG) and use properties established in this connection to aid in 
  clustering and parameter estimation. In particular, we note that the PABM 
  can be represented as latent positions such that points within the same 
  cluster lie on a subspace, and the subspaces that represent each 
  cluster are orthogonal to one another. Using this property as well as the 
  asymptotic properties of Adjacency Spectral Embedding (ASE) of the GRDPG, we 
  are able to establish theoretical asymptotic results of our clustering and 
  parameter estimation methods for the PABM. 
---

>>>>

---
title: "Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation"
output:
  pdf_document:
    citation_package: natbib
    number_sections: yes
# output: html_document
fontsize: 12pt
# geometry: "left=1cm,right=1cm,top=1cm,bottom=1.5cm"
urlcolor: blue
header-includes:
- \usepackage{float}
- \usepackage{mathtools}
- \usepackage{natbib}
- \usepackage[linesnumbered,vlined,ruled]{algorithm2e} 
- \setcitestyle{numbers,square}
- \usepackage{verbatim}
bibliography: misc.bib
abstract: |
  In this paper, we connect two probabilistic models for graphs, the Popularity 
  Adjusted Block Model (PABM) and the Generalized Random Dot Product Graph 
  (GRDPG) and use properties established in this connection to aid in 
  clustering and parameter estimation. In particular, we note that the PABM 
  can be represented as latent positions such that points within the same 
  cluster lie on a subspace, and the subspaces that represent each 
  cluster are orthogonal to one another. Using this property as well as the 
  asymptotic properties of Adjacency Spectral Embedding (ASE) of the GRDPG, we 
  are able to establish theoretical asymptotic results of our clustering and 
  parameter estimation methods for the PABM. 
---
